Surrogate model for aligned-spin binary neutron star waveforms using gaussian process regression

### 2017-07-20 paper/paper.tex
Add comment on comparisons to NR

>>>>

Ref.~\cite{Dietrich:2017feu} carried out comprehensive comparisons of this model to state-of-the-art NR simulations of coalescing nonspinning BNSs with different mass ratios and equations of state, finding that the model can accurately describe the GW phasing up to the last cycle before merger for systems with soft equation of state, while improvements are still needed for systems with stiff equation of state. Similar results hold for the tidal EOB model of Ref.~\cite{Bernuzzi:2014owa}, whose radial potential includes tidal effects in a form that is inspired by first-order gravitational-self-force (GSF) calculations of tidal invariants in the small-mass-ratio limit. Both the EOB model with dynamical tides and the GSF-inspired one are significantly more faithful to NR than the adiabatic tidal EOB model of Refs.~\cite{Damour:2009wj,Bini:2012gu}.
